Blum axioms and nondeterministic computation of functions

### 2016-04-11 paper.tex
paper.tex: Add examples of acceptable Gödel numberings.

>>>>

\begin{example}
    Any encoding of deterministic Turing machines as a binary string
    yields an acceptable numbering of the recursive functions.
    That is, fix one of these encodings;
    define $\pi: \{0, 1\}^* \to \mathcal P$ as follows:
    if the string $w$ encodes the Turing machine $M$,
    $\pi_w$ is the partial function computed by $M$.
\end{example}

\begin{example}\label{c}
    Any programming languages can be understood as an acceptable Gödel numbering.
    For example,
    if we restrict a \texttt C program
    to perform input and output only using the standard input and standard output
    (that is, forbid interactions with the user, file reading, GUIs,
    access to system clock, etc.),
    the resulting program will map a binary input to a binary output,
    characterizing a partial recursive function.
    Thus, we can see a \texttt C compiler
    as an implementation of an acceptable Gödel numbering.\footnote{
        Note we are ignoring here issues like compilation and run-time errors.
        These can be dealt with as in the case of Turing machines:
        any invalid program will signify some fixed partial recursive function
        (say, the function that is defined nowhere);
        and any invalid step in computation
        makes the function to be not defined on that input.
    }
\end{example}

\begin{example}
    We can also think of less orthodox numberings.

    As two-stack deterministic pushdown automata are equivalent to Turing machines%
    ~\cite[p.~172]{HopcroftUllman1979},
    any encoding of these kind of automaton yields acceptable Gödel numberings.

    Unrestricted grammars can also simulate Turing machines%
    ~\cite[p.~221]{HopcroftUllman1979};
    so if a grammar $G$ generate pairs $(x, y)$,
    define the corresponding partial recursive function $f$
    by $f(x) = y$ if,
    among all the pairs whose first element is $x$,
    the pair $(x, y)$ is the one with smallest number of productions
    (leave $f$ undefined if there are ties or no pairs with $x$ as first element).
    (Choosing the pair $(x, y)$ with the smaller number of productions
    allows a Turing machine to simulate this function
    by doing a breadth-first search in the grammar,
    guaranteeing the function is partial recursive.)

    And, as an off-line Turing machine
    (a machine with a special read-only tape for its input)
    can simulate any Turing machine without ever writing a $0$ over a $1$,
    we can associate an encoding of a off-line Turing machine
    with the function that counts the number of times
    it writes a $0$ over an $1$ before halting
    (the number can be converted to binary and have its most significant digit removed
    to generate all possible binary strings).
    (The machine can choose how many times it will write a $0$ over an $1$,
    thus we can generate any partial recursive function by manipulating this choice.)
\end{example}
